---
title: "classification"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen=999)
```

# load packages
```{r}
library(pacman)
pacman::p_load(broom, tidyverse, caret, purrr, data.table, patchwork, install = TRUE)
```

# load and tidy data

Recode continuous scores to the following classes:
< 70 = below clinical range
70 and above = above clinical range

```{r}
# define function to read in files
read_function = function(file) {
  read.csv(file, stringsAsFactors = FALSE) %>%
    mutate(Y_test = ifelse(Y_test < 70, "below", "above"),
           Y_pred_test = ifelse(Y_test < 70, "below", "above"),
           Y_test = as.factor(Y_test),
           Y_pred_test = factor(Y_pred_test, levels = c("above", "below")))
}

# read in files
scores = fs::dir_ls("csv", regexp = ".*csv") %>%
  map_dfr(read_function)

# generate confusion matrices
cmats = scores %>%
  group_by(predictors, outcome, summary, time) %>%
  nest() %>%
  mutate(cmat = map(data, ~ caret::confusionMatrix(.$Y_test, .$Y_pred_test)),
         output = map(cmat, broom::tidy)) %>%
  unnest(output) %>%
  select(-cmat, -data)
```

# plot accuracy

Other metrics that could be plotted instead:

`r unique(cmats$term)`

```{r}
# subset accuracy
accuracy = cmats %>%
  filter(term == "accuracy") %>% 
  ungroup() %>%
  arrange(estimate) %>%
  group_by(outcome) %>%
  mutate(mid = row_number(),
         time = as.character(time)) %>%
  data.table()

# prep data for lower plot panel
model_summary <- unique(accuracy[, c('predictors', 'outcome', 'summary', 'time', 'mid')])
model_summary[, c('summary', 'time') := list(paste0(summary, time), NULL)]
model_summary_l <- melt(model_summary, id.vars = c('outcome', 'mid'))
model_summary_l[, tick := 1]
model_summary_l[, c('variable', 'value') := list(paste(variable, value, sep = '_'), NULL)]
model_summary_w <- dcast(model_summary_l, ... ~ variable, value.var = 'tick', fill = 0)
model_summary_w_l <- melt(model_summary_w, id.vars = c('outcome', 'mid'))

# plot
accuracy %>% 
  ggplot(aes(x = mid, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0) + 
  facet_grid(~ outcome) +
  labs(y = "Accuracy") +
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) + 
ggplot(model_summary_w_l, aes(x = mid, y = variable)) + 
  geom_point(aes(alpha = as.factor(value)), shape = '|', size = 3) +
  scale_alpha_manual(breaks = c(0, 1), values = c(0, 1)) + 
  facet_grid(~ outcome) + 
  theme_minimal() + 
  theme(legend.position = 'none',
        axis.text.x = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = 'Model Property') + 
plot_layout(design = "A\nB")
```
