---
title: "classification"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen=999)
```

# load packages
```{r}
library(pacman)
pacman::p_load(broom, tidyverse, caret, purrr, data.table, patchwork, furrr, install = TRUE)
setDTthreads(4)
future::plan(future::multisession(workers = 4))
```

# load and tidy data

Recode continuous scores to the following classes:
< 70 = below clinical range
70 and above = above clinical range

```{r}
# define function to read in files
read_function = function(file) {
  read.csv(file, stringsAsFactors = FALSE) %>%
    mutate(Y_test_c = ifelse(Y_test < 70, "below", "above"),
           Y_pred_test_c = ifelse(Y_pred_test < 70, "below", "above"),
           Y_test_c = factor(Y_test_c, levels = c("above", "below")),
           Y_pred_test_c = factor(Y_pred_test_c, levels = c("above", "below")))
}

# read in files
scores = fs::dir_ls("csv", regexp = ".*csv") %>%
  future_map_dfr(read_function)

# plots <- scores %>%
#   group_by(predictors, outcome, summary, time) %>%
#   nest() %>%
#   mutate(plot = map(data, ~ ggplot(., aes(x = Y_test, y = Y_pred_test)) +
#                       geom_hex(aes(fill = ..count.., color = ..count..)) + 
#                       geom_hline(yintercept = 70) + 
#                       geom_vline(xintercept = 70) + 
#                       theme_minimal() + 
#                       labs(title = unique(.$fn))))
# 
# distinct(select(scores, predictors, outcome, summary, time))
# 
# filter(plots, predictors == 'pa', outcome == 'overall', summary == 'weekly', time == '1')$plot

# generate confusion matrices
cmats = scores %>%
  group_by(predictors, outcome, summary, time, cv_iter) %>%
  nest() %>%
  mutate(output = map(data, ~ broom::tidy(caret::confusionMatrix(data = .$Y_pred_test_c, reference = .$Y_test_c)))) %>%
  unnest(output) %>%
  select(-data)
```

# plot accuracy

Black is accuracy, red is prevalence.

Other metrics that could be plotted instead:

`r unique(cmats$term)`

```{r}
# subset accuracy
accuracy = cmats %>%
  filter(term == "accuracy") %>% 
  group_by(predictors, outcome, summary, time) %>%
  summarize(mean_qnorm = mean(qnorm(estimate)),
            sd_qnorm = sd(qnorm(estimate)),
            estimate = pnorm(mean_qnorm),
            u = pnorm(mean_qnorm + 2*sd_qnorm),
            l = pnorm(mean_qnorm - 2*sd_qnorm)) %>%
  ungroup() %>%
  arrange(estimate) %>%
  group_by(outcome) %>%
  mutate(mid = row_number(),
         time = as.character(time)) %>%
  data.table()


prevalence = cmats %>%
  filter(term == "prevalence") %>% 
  group_by(predictors, outcome, summary, time) %>%
  summarize(mean_qnorm = mean(qnorm(estimate)),
            sd_qnorm = sd(qnorm(estimate)),
            p_estimate = 1 - pnorm(mean_qnorm),
            p_u = 1 - pnorm(mean_qnorm + 2*sd_qnorm),
            p_l = 1 - pnorm(mean_qnorm - 2*sd_qnorm)) %>%
  mutate(time = as.character(time)) %>%
  data.table()
accuracy = prevalence[, c('predictors', 'outcome', 'summary', 'time', 'p_estimate', 'p_u', 'p_l')][accuracy, on = c('predictors', 'outcome', 'summary', 'time')]

# prep data for lower plot panel
model_summary <- unique(accuracy[, c('predictors', 'outcome', 'summary', 'time', 'mid')])
model_summary[, c('summary', 'time') := list(paste0(summary, time), NULL)]
model_summary_l <- melt(model_summary, id.vars = c('outcome', 'mid'))
model_summary_l[, tick := 1]
model_summary_l[, c('variable', 'value') := list(paste(variable, value, sep = '_'), NULL)]
model_summary_w <- dcast(model_summary_l, ... ~ variable, value.var = 'tick', fill = 0)
model_summary_w_l <- melt(model_summary_w, id.vars = c('outcome', 'mid'))

# plot
accuracy %>% 
  ggplot(aes(x = mid, y = estimate)) + 
  geom_ribbon(aes(ymin = p_l, ymax = p_u), width = 0, color = 'red', alpha = .5) + 
  geom_errorbar(aes(ymin = l, ymax = u), width = 0) + 
  geom_point(size = 1.5) + 
  geom_point(aes(y = p_estimate), color = 'red', size = .75) +
  facet_grid(~ outcome) +
  labs(y = "Accuracy") +
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) + 
ggplot(model_summary_w_l, aes(x = mid, y = variable)) + 
  geom_point(aes(alpha = as.factor(value)), shape = '|', size = 3) +
  scale_alpha_manual(breaks = c(0, 1), values = c(0, 1)) + 
  facet_grid(~ outcome) + 
  theme_minimal() + 
  theme(legend.position = 'none',
        axis.text.x = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = 'Model Property') + 
plot_layout(design = "A\nB")
```

